Towards Transparency and Open Science

### 2023-02-01 manuscript.Rmd
"give us" to "suggest"

Both frameworks show how unaccounted induction leads to overconfidence in empirical results and give us some theoretical tools to asses and control this overconfidence.
Because both frameworks are quite technical, they are followed by a more conceptual summary of these ideas.
These sections provide the basis for understanding how computational reproducibility and preregistration enable a proper assessment of an empirical test on a conceptual level.

>>>>

Both frameworks show how unaccounted induction leads to overconfidence in empirical results and suggest some theoretical tools to asses and control this overconfidence.
Because both frameworks are quite technical, they are followed by a more conceptual summary of these ideas.
These sections provide the basis for understanding how computational reproducibility and preregistration enable a proper assessment of an empirical test on a conceptual level.
